---
title: "Data analysis support for TNC-NTRI rangeland management project publication"
author: "Stefan Gehrig, <a href='https://www.estimact.com'>estimact</a>"
date: "`r format(Sys.time(), '%d %B %Y')`"
subtitle: "Version 1"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    toc_collapsed: TRUE
    toc_depth: 4
    number_sections: FALSE
    css: utils/style.css
    includes:
      after_body: utils/footer.html
bibliography: utils/refs.bib
---

<!-- START OF -->
<br>

***
<!-- DOCUMENT -->

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
```

## Approach

...

All data used can be browsed in the most recent version at <https://stefgehrig.shinyapps.io/TNC-NTRI/>.

<!-- END OF -->
<br>

***
<!-- SECTION -->

## Diagnostic framework variables

....

<!-- END OF -->
<br>

***
<!-- SECTION -->

## Associations of/with outcomes

....

#### Descriptive

....

#### Modelling

....

```{r cars}
cars %>% 
  sample_n(10) %>% 
  kable(
    format = "html",
    caption = "Overview of cars.") %>% 
  kable_styling()
```
<br>

Table \@ref(tab:cars) from @vierus_discovery_2018.

```{r pressure-to-go, fig.align='center', fig.cap='This is a caption.'}
plot(pressure, type = "b")
```
<br>

Plot in Figure \@ref(fig:pressure-to-go).

\begin{equation}
A = (\pi * \lambda \times r^{4}) / \alpha. (\#eq:mean)
\end{equation}
<br>

What we saw in equation \@ref(eq:mean) is obvious.

<!-- END OF -->
<br>

***
<!-- SECTION -->

## Conclusions / Recommendations

<style>
div.blue {background-color:#e6f1fa; border-radius: 5px; padding: 15px;}
</style>
<div class = "blue">

- This is my first conclusion
- This is my second conclusion

</div>

<!-- END OF -->
<br>

***
<!-- SECTION -->

## References
